Parties, Models, Mobsters\newline {\fontsize{11}{15}\selectfont A New Implementation of Model-Based Recursive Partitioning in R}

### 2014-02-07 pkg/partykit/inst/Psychoco-2014/slides.Rnw
some touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@453 255f4249-2263-4417-b1ea-8498779e27a7

\textbf{Required functionality:}
\begin{itemize}
  \item \emph{Parties:} Class and methods for representing recursive partytions.
  \item \emph{Models:} Fitting functions for statistical models (optimizing suitable objective function).
  \item \emph{Mobsters:} High-level interfaces (\code{lmtree()}, \code{bttree()}, \dots)
    that call lower-level \code{mob()} with suitable options and methods.
\end{itemize}

@@

\textbf{Mobsters:}
\begin{itemize}
  \item \code{mob()} already geared towards (generalized) linear models.
  \item Other interfaces in \emph{psychotree} and \emph{betareg}.
  \item Hard to do fine control due to adopted S4 classes: Many unnecessary
    computations and data storage.
\end{itemize}

@@

Data, packages, and \code{estfun()} method.
<<packages, eval=FALSE>>=
data("Topmodel2007", package = "psychotree")
library("partykit")
library("psychotools")
<<estfun.btReg>>
@

@@

\begin{itemize}
  \item All new implementation of model-based recursive partitioning in \emph{partykit}.
  \item Enables more efficient computations, rapid prototyping, customization.
  \item Some new inference options.
\end{itemize}

>>>>

\textbf{Required functionality:}
\begin{itemize}
  \item \emph{Parties:} Class and methods for recursive partytions.
  \item \emph{Models:} Fitting functions for statistical models (optimizing suitable objective function).
  \item \emph{Mobsters:} High-level interfaces (\code{lmtree()}, \code{bttree()}, \dots)
    that call lower-level \code{mob()} with suitable options and methods.
\end{itemize}

@@

\textbf{Mobsters:}
\begin{itemize}
  \item \code{mob()} already geared towards (generalized) linear models.
  \item Other interfaces in \emph{psychotree} and \emph{betareg}.
  \item Hard to do fine control due to adopted S4 classes: Many unnecessary
    computations and copies of data.
\end{itemize}

@@

Data, packages, and \code{estfun()} method:
<<packages, eval=FALSE>>=
data("Topmodel2007", package = "psychotree")
library("partykit")
library("psychotools")
<<estfun.btReg>>
@

@@

\begin{itemize}
  \item All new implementation of model-based recursive partitioning in \emph{partykit}.
  \item Enables more efficient computations, rapid prototyping, flexible customization.
  \item Some new inference options.
\end{itemize}
